A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting

### 2013-09-20 doc/sigchi14/sigchi14.tex
bjoern's pass at overall narrative
more text and figures
various improvements
add ui control screenshots
more refinements
update title
copyright section
changing 'device' to 'appliance, update ui control figures, unuse subcaption package
added names

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{gensymb}
% see http://tex.stackexchange.com/questions/46055/typesetting-with-inch-symbols-and-sizes-in-inches
\usepackage{mathpazo,amsmath}
\def\inch#1{#1''}
\def\ft#1{#1'\thinspace}

@@

%use these commands while writing
\newcommand {\bjoern}[1]{{\color{red}\bf{BH: #1}\normalfont}}
\newcommand {\ben}[1]{{\color{blue}\bf{BZ: #1}\normalfont}}
\newcommand {\sean}[1]{{\color{blue}\bf{SC: #1}\normalfont}}
\newcommand {\claire}[1]{{\color{blue}\bf{CT: #1}\normalfont}}

%comment out the above and uncomment these for final submit
%\newcommand {\bjoern}[1]{}
%\newcommand {\ben}[1]{}
%\newcommand {\sean}[1]{}
%\newcommand {\claire}[1]{}

@@

\title{Selecting and Interacting with Smart Devices Through a Head-Mounted Display with Infrared Targeting}

\numberofauthors{1}
\author{
  \alignauthor Anonymous for submission
%  \alignauthor 3rd Author Name\\
%    \affaddr{Affiliation}\\
%    \affaddr{Address}\\
%    \email{e-mail address}\\
%    \affaddr{Optional phone number}
}

@@

\begin{abstract}
Insert abstract
\end{abstract}

@@

\input{introduction}
\input{relatedwork}
\input{device}
\input{targeting}
\input{control}
\input{conclusion}

>>>>

\toappear{Submitted to CHI2014. Do not cite or distribute without written permission from the authors.}

@@

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{gensymb}
\usepackage{afterpage}
% see http://tex.stackexchange.com/questions/46055/typesetting-with-inch-symbols-and-sizes-in-inches
\usepackage{mathpazo,amsmath}
\def\inch#1{#1''}
\def\ft#1{#1'\thinspace}

@@

%use these commands while writing
\newcommand {\bjoern}[1]{{\color{red}\bf{BH: #1}\normalfont}}
\newcommand {\ben}[1]{{\color{blue}\bf{BZ: #1}\normalfont}}
\newcommand {\sean}[1]{{\color{blue}\bf{SC: #1}\normalfont}}
\newcommand {\claire}[1]{{\color{blue}\bf{CT: #1}\normalfont}}
\newcommand {\studyquote}[1]{\em ``#1''\normalfont}
%comment out the above and uncomment these for final submit
%\newcommand {\bjoern}[1]{}
%\newcommand {\ben}[1]{}
%\newcommand {\sean}[1]{}
%\newcommand {\claire}[1]{}

@@

\title{A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting}

\numberofauthors{1}
\author{
\alignauthor Yu-Hsiang Chen$^{\dagger}$, Ben Zhang$^{\dagger}$, Claire Tuna$^{\dagger}$, Yang Li$^{\ddagger}$, Edward Lee$^{\dagger}$, Bj\"orn Hartmann$^{\dagger}$ \\
\affaddr{$\dagger$: UC Berkeley EECS \& CITRIS Invention Lab \hspace{0.25in} $\ddagger$: Google Research}\\
\email{sean.yhc@gmail.com, benzh@eecs.berkeley.edy, clairetuna@gmail.com, yangli@acm.org, eal@eecs.berkeley.edu, bjoern@eecs.berkeley.edu}
}
%\author{
% \alignauthor Anonymous for submission
%  \alignauthor 3rd Author Name\\
%    \affaddr{Affiliation}\\
%    \affaddr{Address}\\
%    \email{e-mail address}\\
%    \affaddr{Optional phone number}

@@

\begin{abstract}
\input{abstract}
\end{abstract}

@@

\input{introduction}
\input{relatedwork}
\input{interaction}
\input{device}
\input{targeting}
\input{control}
\input{discussion}
\input{conclusion}
\section{Acknowledgments}
This work was partially supported by a Sloan Foundation Fellowship.
